gij bent 2

### 2025-09-30 paper/paper.qmd
Finish conclusion, more or less

This article aimed to investigate whether and how speakers deviate from general expectations. We focussed on the affordances these deviations, defined as individual variation, can bring for alternation research, as well as what implicit network structures can teach us about the spread of linguistic innovations. We looked into the choice between the conservative *gij zijt* and the innovative *gij bent* in Colloquial Belgian Dutch with a dataset based on `r num_tweets_filtered %>% formatn` tweets by `r num_users_filtered %>% formatn` authors. By having several attestations from the same authors, we were able to devise a "linguistic profile" for each author, quantifying their behaviour with regards to expectations based on more general factors like gender and dialect region. Through elastic net regression, a modern regression technique, deviations were found for TODO users in the dataset (TODO percent). TODO more conservative, TODO more innovative We also found a regional pattern in the deviations, with the central Brabant region differing from the other Flemish dialects. The Brabant region deviates towards the innovative form, the other regions deviate towards the conservative form. We also found a geospatial pattern, spanning horizontally, which shows a potential future path for the diffusion of the innovative form.

@@

The predictive nature of the geospatial distributions bring us to the network analysis of our study. Our results show that the socially influential users in our dataset are generally more innovative. This might indicate that the diffusion of the innovative *bent* variant is in the TODO phase.

>>>>

This article aimed to investigate whether and how speakers deviate from general expectations. We focussed on the affordances these deviations, defined as individual variation, can bring for alternation research, as well as what implicit network structures can teach us about the spread of linguistic innovations. We looked into the choice between the conservative *gij zijt* and the innovative *gij bent* in Colloquial Belgian Dutch with a dataset based on `r num_tweets_filtered %>% formatn` tweets by `r num_users_filtered %>% formatn` authors. By having several attestations from the same authors, we were able to devise a "linguistic profile" for each author, quantifying their behaviour with regards to expectations based on more general factors like gender and dialect region. Through elastic net regression, a modern regression technique, deviations were found for `r non_eliminated_count %>% formatn` users in the dataset (`r removed_distribution_prop[["FALSE"]] %>% formatp` of authors). `r innovative_count %>% formatn` (`r non_zero_distribution_prop[["innovative"]] %>% formatp`) were innovative, while `r conservative_count %>% formatn` (`r non_zero_distribution_prop[["conservative"]] %>% formatp`) were conservative. We also found a regional pattern in the deviations, with the central Brabant region differing from the other Flemish dialects. The Brabant region correct towards the innovative form, the other regions correct towards the conservative form. We also found a geospatial pattern, spanning horizontally, which shows a potential future path for the diffusion of the innovative form.

@@

The predictive nature of the geospatial distributions bring us to the network analysis of our study. Our results show that the socially influential users in our dataset are generally more innovative. This might indicate that the diffusion of the innovative *bent* variant might be currently in the "early adopters" stage. The innovative variant can therefore be assumed to diffuse more broadly in the future. Of course, it remains to be seen just how accurate the network measure is for accurately predicting the current stage in the diffusion of an innovation. A diachronic network study of a fully completed diffusion pattern could shed more light in this regard.

Finally, our study shows that CBD is still very much "in flux". While one cannot speak of a single, monolithic CBD variety, the geospatial findings suggest that a horizontal expansion of at least this Antwerp-Brabantian feature could be possible. This would go against previous findings arguing against the "Brabant expansion", but it is not unthinkable when one takes the perspective of individual variation. As was mentioned in @sec-introduction, individual linguistic behaviour is not uniformly progressive or conservative. An uneven diffusion of CBD features might find its roots in this non-uniform individual behaviour.
